Untitled

### 2023-10-27 code/analysis_Redo.Rmd
more figure updates

p.desc <- ggarrange(plot1, plot0)

@@

ggsave(filename = "Picture1.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 16, height = 9)

@@

p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, nrow = 1 ) 
p0

@@

)

@@

zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)
zp <- ggarrange(zp3, zp4, common.legend = TRUE)
zp

@@

@@

ggsave(filename = "Picture11.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = mapps, width = 16, height = 9)
```

@@

## All Hypotheses tested
data.frame(rbind(did.core, did.select.stint, did.select.payer, did.rival)) %>% 
  rbind(TEs) %>% rbind(TEs_Dist) %>% 
  arrange(`Pr...t..`) %>% 
  cbind(c(1:43) / 43 * 0.1) %>% 
  mutate(Row = row_number()) %>% 
  ggplot(aes(x = Row, y = `Pr...t..`)) + geom_point() + 
  ylab("p-values") + xlab("Significance Rank") + geom_abline(slope = 1/43 * 0.1, intercept = 0, color="red", linetype="dashed", alpha=.5) + theme_minimal()

>>>>

p.desc <- ggarrange(plot1, plot0, ncol = 1)

@@

ggsave(filename = "Picture1.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = p.desc, width = 11, height = 15)

@@

p0 <- ggarrange(
  event_study(data = df.core, 
  yname = "Total", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients") + xlab("Year Relative to Competitive Shock") + ylab("Number of Patients"), 
event_study(data = df.core, 
  yname = "Qcomp", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Quality Composite")+ xlab("Year Relative to Competitive Shock") + ylab("Percentage Points"), 
event_study(data = df.core, 
  yname = "Altman", idname = "ID", tname = "Year", gname = "Att", estimator = "all", xformla = ~Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless) %>% 
  filter(abs(term) <= 5) %>% 
  filter(estimator == "Gardner (2021)") %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5)  + ggtitle("Financial Resilience") + xlab("Year Relative to Competitive Shock") + ylab("Risk Units"), common.legend = TRUE, ncol = 1 ) 
p0

@@

@@

zp <- ggarrange(zp1, zp2, zp3, zp4, common.legend = TRUE)
zp <- ggarrange(zp3, zp4, common.legend = TRUE)

@@

#ggsave(filename = "Picture13.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = zp, width = 16, height = 9)
```

@@

#ggsave(filename = "Picture11.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = mapps, width = 16, height = 9)
```

@@

## All Hypotheses tested
bhoch <- data.frame(rbind(did.core, did.select.stint, did.select.payer, did.rival)) %>% 
  rbind(TEs) %>% rbind(TEs_Dist) %>% 
  arrange(`Pr...t..`) %>% 
  cbind(c(1:43) / 43 * 0.1) %>% 
  mutate(Row = row_number()) %>% 
  ggplot(aes(x = Row, y = `Pr...t..`)) + geom_point() + 
  ylab("p-values") + xlab("Significance Rank") + geom_abline(slope = 1/43 * 0.1, intercept = 0, color="red", linetype="dashed", alpha=.5) + theme_minimal()

#ggsave(filename = "Picture12.png", path = "/Users/jhm65/Dropbox/Writing/JMP_figures", plot = bhoch, width = 16, height = 9)
